---
title: "Untitled"
output: bookdown::pdf_document2
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
library("worcs")
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
load_data()
knitr::opts_chunk$set(echo = FALSE, wawarning = FALSE, message= FALSE)
```

This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency. All code <!--and data--> are available at <git@github.com:cjvanlissa/worcs_oscoffee.git>.

This is an example of a non-essential citation [@vanlissaWORCSWorkflowOpen2020]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

<!--The function below inserts a notification if the manuscript is knit using synthetic data. Make sure to insert it after load_data().-->
`r notify_synthetic()`

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
library(tidySEM)
library(lavaan)
tab_desc <- descriptives(df)
knitr::kable(tab_desc)
```

## Analysis

```{r}
mod <- "
vis =~ vis_1 + vis_2 + vis_3
tex =~ tex_1 + tex_2 + tex_3
speed =~ spe_1 + spe_2 + spe_3
"

res <- cfa(mod, df)
knitr::kable(table_results(res, columns = c("mplus_label", "est_sig", 
"confint", "est_std", "confint_std")))
```

## Picture

```{r tmp, fig.cap="Bla"}
lay <- get_layout("",       "tex",    "",       "",     "vis",   "",     ""   , "speed", "", 
                  "tex_1", "tex_2", "tex_3", "vis_1", "vis_2", "vis_3","spe_1", "spe_2", "spe_3",
                  rows = 2)
graph_sem(res, layout = lay, fix_coord = TRUE)
```


